Automatic Matching of Bullet Lands

### 2016-05-07 imaging-paper.Rnw
Few smaller typos

The purpose of our paper is to present an automatic matching routine that allows for a completely objective assessment of the quality of a match. 
The original paper on the complete Hamby study already reports the successful use of several computer-assisted methods; aside from a zero false positive rate no further details on a false-negative error rate for bullets are given nor are error rates for land-to-land matches mentioned. 
% Hamby study: automated systems were successfully used for matching:
%  Intelligent Automation's SciClops - Dr. Ben Bachrach (Maryland, United States);
% Automated Land Identification System (ALIS) - Mr. Tsuneo Uchiyama (Tokyo, Japan);
% Integrated Ballistics Identification System (IBIS) – Mr. Robert Thompson (California, United States);
% BulletTRAX-3DTM - Forensic Technology Scientists (Montreal, Canada) (2 sets)

@@

In an approach to analyze the striation pattern we extract a \emph{bullet profile} \citep{ma:2004} by taking a cross section of the surface measurements at a fixed height $x$ along the bullet land.
%An initial naive approach to analyzing the striation patterns leads us to fixing a particular value of a coordinate, and then producing a plot of the surface measurements across. 
Figure \ref{fig:fixedX} shows a plot of the side profile of a bullet land. It can be seen that the global structure of the land dominates the appearance of the plot. The grooves can be clearly identified on the left and right side, and the curvature of the surface is the most visible feature in the middle.

@@

\subsection{Identifying groove locations}
%In an attempt to improve upon the previous algorithm, w
We first have to identify the locations of the left and right groove in the image. The grooves are assumed to not contain information relevant for determining matches. They also dominate the structure, and therefore need  to be removed.  
Fortunately, the location and appearance of the grooves in the surface profiles is quite consistent.
Surface measurements reach local maxima around the peak of the groove at either end of the range of $y$, we can then follow the descent of the surface measurements inwards to the valley of the groove. 
The location of the valleys  mark the points at which we should trim the image. The procedure can be described as follows:

>>>>

The purpose of our paper is to present an automatic matching routine that allows for a completely objective assessment of the quality of a match. 
The original paper on the complete Hamby study already reports the successful use of several computer-assisted methods; aside from a zero false positive rate, no further details on a false-negative error rate for bullets are given nor are error rates for land-to-land matches mentioned. 
% Hamby study: automated systems were successfully used for matching:
%  Intelligent Automation's SciClops - Dr. Ben Bachrach (Maryland, United States);
% Automated Land Identification System (ALIS) - Mr. Tsuneo Uchiyama (Tokyo, Japan);
% Integrated Ballistics Identification System (IBIS) – Mr. Robert Thompson (California, United States);
% BulletTRAX-3DTM - Forensic Technology Scientists (Montreal, Canada) (2 sets)

@@

In an approach to analyze the striation pattern, we extract a \emph{bullet profile} \citep{ma:2004} by taking a cross section of the surface measurements at a fixed height $x$ along the bullet land.
%An initial naive approach to analyzing the striation patterns leads us to fixing a particular value of a coordinate, and then producing a plot of the surface measurements across. 
Figure \ref{fig:fixedX} shows a plot of the side profile of a bullet land. It can be seen that the global structure of the land dominates the appearance of the plot. The grooves can be clearly identified on the left and right side, and the curvature of the surface is the most visible feature in the middle.

@@

\subsection{Identifying groove locations}
%In an attempt to improve upon the previous algorithm, w
We first have to identify the locations of the left and right groove in the image. The grooves are assumed to contain no information relevant for determining matches. They also dominate the structure, and therefore need to be removed.  
Fortunately, the location and appearance of the grooves in the surface profiles is quite consistent.
Surface measurements reach local maxima around the peak of the groove at either end of the range of $y$, we can then follow the descent of the surface measurements inwards to the valley of the groove. 
The location of the valleys mark the points at which we should trim the image. The procedure can be described as follows:
